---
title: "LAAR Dashboard - v01"
output: html_notebook
---

## Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
set.seed(42)

```


## Import packages
```{r load packages, warning=FALSE, message=FALSE}
library(tidyverse)
theme_set(theme_classic())
library(jsonlite)
library(lubridate)

```


## Load data
```{r}
statements_raw <- stream_in(file("trussApp.json"))

```


## Explore and prepare data

Show variable names
```{r}
names(statements_raw)
```

Filter data to week of PLS and relevant variables
```{r}
statements_pls <- statements_raw %>% 
  filter(timestamp >= "2019-04-01") %>% 
  filter(timestamp <= "2019-04-05") %>% 
  select('_id', timestamp, statement)

```

Flatten nested JSON structure to data frame, select relevant variables, make object IDs prettier
```{r}
statements_pls_flat <- statements_pls %>%
  flatten() %>% 
  select(timestamp, 
         statement.actor.account.name,
         statement.actor.name,
         'statement.verb.display.en-US',
         statement.object.id
         ) %>% 
  mutate(
    statement.object.id = str_replace(statement.object.id, 'http://example.com/', ''),
    statement.object.id = str_replace(statement.object.id, 'http://activitystrea.ms/schema/1.0/', ''),
    event = str_c(statement.actor.name, " ", `statement.verb.display.en-US`, " ", statement.object.id)
  )


```

Split data into trainer and trainee datasets
```{r}
statements_pls_flat_trainee <- statements_pls_flat %>% 
  filter(statement.actor.name == "Trainee")

statements_pls_flat_trainer <- statements_pls_flat %>% 
  filter(statement.actor.name == "Trainer")

```

### Trainee data

Filter out irrelevant records
```{r}
statements_pls_flat_trainee <- statements_pls_flat_trainee %>% 
  filter(statement.object.id != "application")

```

Transform data from long to wide
```{r, warning=FALSE}

statements_pls_flat_trainee_wide <- statements_pls_flat_trainee %>% 
  pivot_wider(names_from = event, values_from = timestamp, values_fn = list(timestamp = min)) %>%
  select(-'statement.verb.display.en-US', -statement.object.id, -statement.actor.name) %>% 
  group_by(statement.actor.account.name) %>% 
  summarise_all(max, na.rm=TRUE)

statements_pls_flat_trainee_wide <- statements_pls_flat_trainee_wide %>% 
  mutate(
    session = statement.actor.account.name,
    aborted_node_1 = ifelse(year(`Trainee skipped node/1`) != 2019 & year(`Trainee passed node/1`) != 2019, 1, 0),
    aborted_node_2 = ifelse(year(`Trainee skipped node/2`) != 2019 & year(`Trainee passed node/2`) != 2019, 1, 0),
    aborted_node_3 = ifelse(year(`Trainee skipped node/3`) != 2019 & year(`Trainee passed node/3`) != 2019, 1, 0),
    aborted_node_4 = ifelse(year(`Trainee skipped node/4`) != 2019 & year(`Trainee passed node/4`) != 2019, 1, 0),
    aborted_node_5 = ifelse(year(`Trainee skipped node/5`) != 2019 & year(`Trainee passed node/5`) != 2019, 1, 0),
    aborted_node_6 = ifelse(year(`Trainee skipped node/6`) != 2019 & year(`Trainee passed node/6`) != 2019, 1, 0),
    skipped_node_1 = year(`Trainee skipped node/1`) == 2019,
    skipped_node_1 = ifelse(is.na(skipped_node_1), 0, 1),
    skipped_node_2 = year(`Trainee skipped node/2`) == 2019,
    skipped_node_2 = ifelse(is.na(skipped_node_2), 0, 1),
    skipped_node_3 = year(`Trainee skipped node/3`) == 2019,
    skipped_node_3 = ifelse(is.na(skipped_node_3), 0, 1),
    skipped_node_4 = year(`Trainee skipped node/4`) == 2019,
    skipped_node_4 = ifelse(is.na(skipped_node_4), 0, 1),
    skipped_node_5 = year(`Trainee skipped node/5`) == 2019,
    skipped_node_5 = ifelse(is.na(skipped_node_5), 0, 1),
    skipped_node_6 = year(`Trainee skipped node/6`) == 2019,
    skipped_node_6 = ifelse(is.na(skipped_node_6), 0, 1),
    nodes_skipped =  skipped_node_1 + skipped_node_2 + skipped_node_3 + skipped_node_4 + skipped_node_5 + skipped_node_6
  ) %>% 
  filter(
    !is.na(aborted_node_1)
  ) %>% 
  filter(
    !is.na(aborted_node_2)
  ) %>% 
  filter(
    !is.na(aborted_node_3)
  ) %>% 
  filter(
    !is.na(aborted_node_4)
  ) %>% 
  filter(
    !is.na(aborted_node_5)
  ) %>% 
  filter(
    !is.na(aborted_node_6)
  ) %>% 
  select(
    session,
    skipped_node_1, skipped_node_2, skipped_node_3, skipped_node_4, skipped_node_5, skipped_node_6,
    nodes_skipped,
    'Trainee launched node/1',      
    #'Trainee viewed node/1',    
    'Trainee attempted node/1',    
    'Trainee skipped node/1',       
    'Trainee passed node/1',      
    #'Trainee failed node/1',
    #'Trainee finished node/1',
    'Trainee launched node/2',     
    #'Trainee viewed node/2',        
    'Trainee attempted node/2',     
    'Trainee skipped node/2',      
    'Trainee passed node/2',     
    #'Trainee failed node/2',
    #'Trainee finished node/2',
    'Trainee launched node/3',     
    #'Trainee viewed node/3',       
    'Trainee attempted node/3',    
    'Trainee skipped node/3',     
    'Trainee passed node/3',       
    #'Trainee failed node/3',
    #'Trainee finished node/3',
    'Trainee launched node/4',    
    #'Trainee viewed node/4',       
    'Trainee attempted node/4',    
    'Trainee skipped node/4',      
    'Trainee passed node/4',       
    #'Trainee failed node/4',
    #'Trainee finished node/4',
    'Trainee launched node/5',     
    #'Trainee viewed node/5',      
    'Trainee attempted node/5',    
    'Trainee skipped node/5',       
    'Trainee passed node/5',      
    #'Trainee failed node/5',
    #'Trainee finished node/5',
    'Trainee launched node/6',     
    #'Trainee viewed node/6',       
    'Trainee attempted node/6',    
    'Trainee skipped node/6',     
    'Trainee passed node/6',
    #'Trainee failed node/6'
    #'Trainee finished node/6'
  )

```

Calculate activity times
```{r}
time_for_node <- function(df, node){
  result <- case_when(
    node == 1 ~ df$'Trainee launched node/2' - df$'Trainee launched node/1',
    node == 2 ~ df$'Trainee launched node/3' - df$'Trainee launched node/2',
    node == 3 ~ df$'Trainee launched node/4' - df$'Trainee launched node/3',
    node == 4 ~ df$'Trainee launched node/5' - df$'Trainee launched node/4',
    node == 5 ~ df$'Trainee launched node/6' - df$'Trainee launched node/5',
    node == 6 ~ df$'Trainee passed node/6' - df$'Trainee launched node/6',
    TRUE ~ df$'Trainee passed node/1' - df$'Trainee launched node/1'
    )
  return(result)
  }

statements_pls_flat_trainee_wide$time_for_node_1 <- time_for_node(statements_pls_flat_trainee_wide, 1)
statements_pls_flat_trainee_wide$time_for_node_2 <- time_for_node(statements_pls_flat_trainee_wide, 2)
statements_pls_flat_trainee_wide$time_for_node_3 <- time_for_node(statements_pls_flat_trainee_wide, 3)
statements_pls_flat_trainee_wide$time_for_node_4 <- time_for_node(statements_pls_flat_trainee_wide, 4)
statements_pls_flat_trainee_wide$time_for_node_5 <- time_for_node(statements_pls_flat_trainee_wide, 5)
statements_pls_flat_trainee_wide$time_for_node_6 <- time_for_node(statements_pls_flat_trainee_wide, 6)
```

Add column indicating whether learning sequence has been completed from start to end
```{r}
statements_pls_flat_trainee_wide$sequence_completed <- ifelse(statements_pls_flat_trainee_wide$time_for_node_6 > 0, TRUE, FALSE) 
statements_pls_flat_trainee_wide$sequence_completed <- replace_na(statements_pls_flat_trainee_wide$sequence_completed, FALSE)
```

Add columns indicating whether single activities have been skipped by learner
```{r}
statements_pls_flat_trainee_wide <- statements_pls_flat_trainee_wide %>% 
  mutate(
    skipped_corner_1 = skipped_node_1 + skipped_node_2 + skipped_node_3,  
    skipped_corner_1 = ifelse(skipped_corner_1 == 0, 0, 1),
    skipped_corner_2 = skipped_node_4,
    skipped_corner_3 = skipped_node_5,
    skipped_corner_4 = skipped_node_6,
    time_for_corner_1 = time_for_node_1 + time_for_node_2 + time_for_node_3,
    time_for_corner_2 = time_for_node_4,
    time_for_corner_3 = time_for_node_5,
    time_for_corner_4 = time_for_node_6
  )

```

### Trainer data

Filter out irrelavant records and transform some columns
```{r}
statements_pls_flat_trainer <- statements_pls_flat_trainer %>% 
  filter(statement.object.id != "application") %>% 
  filter(`statement.verb.display.en-US` != "evaluated") %>%
  mutate(
    session = statement.actor.account.name,
    success = ifelse(`statement.verb.display.en-US` == "accepted", 1, 0),
    node = str_sub(statement.object.id, 1, 6) 
  )

```

Group and summarise data by user and node
```{r}
statements_pls_flat_trainer_g1 <- statements_pls_flat_trainer %>% 
  group_by(session, node) %>% 
  summarise(
    score = round(mean(success) * 2, digits = 2),
    score = ifelse(score > 1, 1, score)
  )

statements_pls_flat_trainer_g2 <- statements_pls_flat_trainer %>% 
  filter(node == "node/4") %>% 
  group_by(session, statement.object.id) %>% 
  summarise(
    score = round(mean(success) * 2, digits = 2),
    score = ifelse(score > 1, 1, score)
  )


```

From long to wide
```{r}
statements_pls_flat_trainer_g1_wide <- statements_pls_flat_trainer_g1 %>% 
  pivot_wider(names_from = node, values_from = score) %>% 
  mutate(
    score_node_1 = replace_na(`node/1`, 0),
    score_node_2 = replace_na(`node/2`, 0),
    score_node_3 = replace_na(`node/3`, 0),
    score_node_4 = replace_na(`node/4`, 0),
    score_node_5 = replace_na(`node/5`, 0),
    score_node_6 = replace_na(`node/6`, 0),
    score_corner_1 = mean(score_node_1, score_node_2, score_node_3),
    score_corner_2 = score_node_4,
    score_corner_3 = score_node_5,
    score_corner_4 = score_node_6,
    overall_score = mean(score_corner_1, score_corner_2, score_corner_3, score_corner_4)
  ) %>% 
  select(
    session,
    score_corner_1, score_corner_2, score_corner_3, score_corner_4,
    overall_score
  )

statements_pls_flat_trainer_g2_wide <- statements_pls_flat_trainer_g2 %>% 
  pivot_wider(names_from = statement.object.id, values_from = score) %>% 
  mutate_all(round) %>% 
  ungroup() %>% 
  transmute(
    session = session,
    score_activity_01 = `node/4/checklistitem/0`,
    score_activity_02 = `node/4/checklistitem/1`,
    score_activity_03 = `node/4/checklistitem/2`,
    score_activity_04 = `node/4/checklistitem/3`,
    score_activity_05 = `node/4/checklistitem/4`,
    score_activity_06 = `node/4/checklistitem/5`,
    score_activity_07 = `node/4/checklistitem/6`,
    score_activity_08 = `node/4/checklistitem/7`,
    score_activity_09 = `node/4/checklistitem/8`,
    score_activity_10 = `node/4/checklistitem/9`,
    score_activity_11 = `node/4/checklistitem/10`,
    score_activity_12 = `node/4/checklistitem/11`,
    score_activity_13 = `node/4/checklistitem/12`,
    score_activity_14 = `node/4/checklistitem/13`
  )

```


## Join Trainee and Trainer data
```{r}
joined <- statements_pls_flat_trainee_wide %>% 
  inner_join(statements_pls_flat_trainer_g1_wide, by = "session") %>% 
  inner_join(statements_pls_flat_trainer_g2_wide, by = "session")

```


## Visualization: Trainer Dashboard

### Time

```{r}
joined <- joined %>% 
  mutate(
    time_for_corner_4 = ifelse(is.infinite(time_for_corner_4), NA, time_for_corner_4),
    score_competence_10_02 = (score_activity_03 + score_activity_04 + score_activity_07 + score_activity_10 + score_activity_13)/5,
    score_competence_10_03 = (score_activity_01 + score_activity_02 + score_activity_06 + score_activity_12)/4,
    score_competence_10_04 = score_activity_11,
    score_competence_10_05 = (score_activity_05 + score_activity_09)/2,
    score_competence_10_08 = score_activity_14,
    score_competence_10_10 = score_activity_08
  )

joined_s <- joined %>% 
  summarise(
    time_for_corner_1_avg = mean(time_for_corner_1),
    time_for_corner_2_avg = mean(time_for_corner_2),
    time_for_corner_3_avg = mean(time_for_corner_3),
    time_for_corner_4_avg = mean(time_for_corner_4, na.rm = TRUE),
    time_for_corner_1_sd = sd(time_for_corner_1),
    time_for_corner_2_sd = sd(time_for_corner_2),
    time_for_corner_3_sd = sd(time_for_corner_3),
    time_for_corner_4_sd = sd(time_for_corner_4, na.rm = TRUE),
    overall_score_avg = mean(overall_score),
    score_corner_1_avg = mean(score_corner_1),
    score_corner_2_avg = mean(score_corner_2),
    score_corner_3_avg = mean(score_corner_3),
    score_corner_4_avg = mean(score_corner_4),
    score_activity_01_avg = mean(score_activity_01),
    score_activity_02_avg = mean(score_activity_02),
    score_activity_03_avg = mean(score_activity_03),
    score_activity_04_avg = mean(score_activity_04),
    score_activity_05_avg = mean(score_activity_05),
    score_activity_06_avg = mean(score_activity_06),
    score_activity_07_avg = mean(score_activity_07),
    score_activity_08_avg = mean(score_activity_08),
    score_activity_09_avg = mean(score_activity_09),
    score_activity_10_avg = mean(score_activity_10),
    score_activity_11_avg = mean(score_activity_11),
    score_activity_12_avg = mean(score_activity_12),
    score_activity_13_avg = mean(score_activity_13),
    score_activity_14_avg = mean(score_activity_14),
    score_competence_10_02_avg = mean(score_competence_10_02),
    score_competence_10_03_avg = mean(score_competence_10_03),
    score_competence_10_04_avg = mean(score_competence_10_04),
    score_competence_10_05_avg = mean(score_competence_10_05),
    score_competence_10_08_avg = mean(score_competence_10_08),
    score_competence_10_10_avg = mean(score_competence_10_10)
  )

write_csv(joined, "joined.csv")
#joined <- read_csv("joined.csv")

write_csv(joined_s, "joined_s.csv")
#joined_s <- read_csv("joined_s.csv")

```


```{r}
ggplot(data=joined_s) +
  geom_col(mapping = aes(x="#1", y=time_for_corner_1_avg)) +
  geom_col(mapping = aes(x="#2", y=time_for_corner_2_avg)) +
  geom_col(mapping = aes(x="#3", y=time_for_corner_3_avg)) +
  geom_col(mapping = aes(x="#4", y=time_for_corner_4_avg)) +
  geom_errorbar(mapping = aes(x="#1", ymin=time_for_corner_1_avg - time_for_corner_1_sd, ymax=time_for_corner_1_avg + time_for_corner_1_sd), width = 0.2) +
  geom_errorbar(mapping = aes(x="#2", ymin=time_for_corner_2_avg - time_for_corner_2_sd, ymax=time_for_corner_2_avg + time_for_corner_2_sd), width = 0.2) +
  geom_errorbar(mapping = aes(x="#3", ymin=time_for_corner_3_avg - time_for_corner_3_sd, ymax=time_for_corner_3_avg + time_for_corner_3_sd), width = 0.2) +
  geom_errorbar(mapping = aes(x="#4", ymin=time_for_corner_4_avg - time_for_corner_4_sd, ymax=time_for_corner_4_avg + time_for_corner_4_sd), width = 0.2) +
  scale_x_discrete(name = "Truss Corner") +
  scale_y_continuous(limits = c(0, 300), name = "Time (in sec.)")

```


```{r}
ggplot(data=joined) +
  geom_histogram(mapping = aes(x=time_for_corner_1)) +
  scale_x_continuous(limits = c(0, 300), name = "Time (in sec.)") +
  ylab("Number of trainees") +
  ggtitle("Truss Corner #1")

ggplot(data=joined) +
  geom_histogram(mapping = aes(x=time_for_corner_2)) +
  scale_x_continuous(limits = c(0, 300), name = "Time (in sec.)") +
  ylab("Number of trainees") +
  ggtitle("Truss Corner #2")

ggplot(data=joined) +
  geom_histogram(mapping = aes(x=time_for_corner_3)) +
  scale_x_continuous(limits = c(0, 300), name = "Time (in sec.)") +
  ylab("Number of trainees") +
  ggtitle("Truss Corner #3")

ggplot(data=joined) +
  geom_histogram(mapping = aes(x=time_for_corner_4)) +
  scale_x_continuous(limits = c(0, 300), name = "Time (in sec.)") +
  ylab("Number of trainees") +
  ggtitle("Truss Corner #4")
 
```

### Errors

Score per corner
```{r}
ggplot(data=joined_s) +
  geom_col(mapping = aes(x="#1", y=score_corner_1_avg)) +
  geom_col(mapping = aes(x="#2", y=score_corner_2_avg)) +
  geom_col(mapping = aes(x="#3", y=score_corner_3_avg)) +
  geom_col(mapping = aes(x="#4", y=score_corner_4_avg)) +
  scale_x_discrete(name = "Truss Corner") +
  scale_y_continuous(limits = c(0, 1), name = "Score") +
  ggtitle("Average score")


```

Score per activity
```{r}
ggplot(data=joined_s) +
  geom_col(mapping = aes(x="#01: Take egg", y=score_activity_01_avg)) +
  geom_col(mapping = aes(x="#02: Choose egg of correct size", y=score_activity_02_avg)) +
  geom_col(mapping = aes(x="#03: Check egg for outside damage", y=score_activity_03_avg)) +
  geom_col(mapping = aes(x="#04: Check egg for inside damage", y=score_activity_04_avg)) +
  geom_col(mapping = aes(x="#05: Place egg in right direction", y=score_activity_05_avg)) +
  geom_col(mapping = aes(x="#06: Take correct pivot", y=score_activity_06_avg)) +
  geom_col(mapping = aes(x="#07: Check pivot for damage", y=score_activity_07_avg)) +
  geom_col(mapping = aes(x="#08: Disposed damaged pivot, if needed", y=score_activity_08_avg)) +
  geom_col(mapping = aes(x="#09: Place pivot in right direction", y=score_activity_09_avg)) +
  geom_col(mapping = aes(x="#10: Check if pivot fits", y=score_activity_10_avg)) +
  geom_col(mapping = aes(x="#11: Wobble or hammer pivot, if needed", y=score_activity_11_avg)) +
  geom_col(mapping = aes(x="#12: Choose correct splint pen", y=score_activity_12_avg)) +
  geom_col(mapping = aes(x="#13: Check if split pen closes properly", y=score_activity_13_avg)) +
  geom_col(mapping = aes(x="#14: Put splint pen into pivot", y=score_activity_14_avg)) +
  geom_text(mapping = aes(x="#01: Take egg", y=score_activity_01_avg, label=round(score_activity_01_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#02: Choose egg of correct size", y=score_activity_02_avg, label=round(score_activity_02_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#03: Check egg for outside damage", y=score_activity_03_avg, label=round(score_activity_03_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#04: Check egg for inside damage", y=score_activity_04_avg, label=round(score_activity_04_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#05: Place egg in right direction", y=score_activity_05_avg, label=round(score_activity_05_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#06: Take correct pivot", y=score_activity_06_avg, label=round(score_activity_06_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#07: Check pivot for damage", y=score_activity_07_avg, label=round(score_activity_07_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#08: Disposed damaged pivot, if needed", y=score_activity_08_avg, label=round(score_activity_08_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#09: Place pivot in right direction", y=score_activity_09_avg, label=round(score_activity_09_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#10: Check if pivot fits", y=score_activity_10_avg, label=round(score_activity_10_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#11: Wobble or hammer pivot, if needed", y=score_activity_11_avg, label=round(score_activity_11_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#12: Choose correct splint pen", y=score_activity_12_avg, label=round(score_activity_12_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#13: Check if split pen closes properly", y=score_activity_13_avg, label=round(score_activity_13_avg,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#14: Put splint pen into pivot", y=score_activity_14_avg, label=round(score_activity_14_avg,2)), vjust=1.6, color="white") +
  scale_x_discrete(name = "Activity") +
  scale_y_continuous(limits = c(0, 1), name = "Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Average score per activity (measured on Truss Corner #2)")

```


## Visualization: Trainee Dashboard

```{r}
one_session <- filter(joined, session == "AULWB")

```

### Time

```{r}
ggplot(data=one_session) +
  geom_col(mapping = aes(x="#1", y=time_for_corner_1)) +
  geom_col(mapping = aes(x="#2", y=time_for_corner_2)) +
  geom_col(mapping = aes(x="#3", y=time_for_corner_3)) +
  geom_col(mapping = aes(x="#4", y=time_for_corner_4)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#1", ymin=time_for_corner_1_avg, ymax=time_for_corner_1_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#2", ymin=time_for_corner_2_avg, ymax=time_for_corner_2_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#3", ymin=time_for_corner_3_avg, ymax=time_for_corner_3_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#4", ymin=time_for_corner_4_avg, ymax=time_for_corner_4_avg)) +
  scale_x_discrete(name = "Truss Corner") +
  scale_y_continuous(limits = c(0, 300), name = "Time (in sec.)")
  
```

### Errors

Score per corner
```{r}
ggplot(data=one_session) +
  geom_col(mapping = aes(x="#1", y=score_corner_1)) +
  geom_col(mapping = aes(x="#2", y=score_corner_2)) +
  geom_col(mapping = aes(x="#3", y=score_corner_3)) +
  geom_col(mapping = aes(x="#4", y=score_corner_4)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#1", ymin=score_corner_1_avg, ymax=score_corner_1_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#2", ymin=score_corner_2_avg, ymax=score_corner_2_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#3", ymin=score_corner_3_avg, ymax=score_corner_3_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#4", ymin=score_corner_4_avg, ymax=score_corner_4_avg)) +
  scale_x_discrete(name = "Truss Corner") +
  scale_y_continuous(limits = c(0, 1), name = "Score") +
  ggtitle("Average score")

```


Score per activity
```{r}
ggplot(data=one_session) +
  geom_col(mapping = aes(x="#01: Take egg", y=score_activity_01)) +
  geom_col(mapping = aes(x="#02: Choose egg of correct size", y=score_activity_02)) +
  geom_col(mapping = aes(x="#03: Check egg for outside damage", y=score_activity_03)) +
  geom_col(mapping = aes(x="#04: Check egg for inside damage", y=score_activity_04)) +
  geom_col(mapping = aes(x="#05: Place egg in right direction", y=score_activity_05)) +
  geom_col(mapping = aes(x="#06: Take correct pivot", y=score_activity_06)) +
  geom_col(mapping = aes(x="#07: Check pivot for damage", y=score_activity_07)) +
  geom_col(mapping = aes(x="#08: Disposed damaged pivot, if needed", y=score_activity_08)) +
  geom_col(mapping = aes(x="#09: Place pivot in right direction", y=score_activity_09)) +
  geom_col(mapping = aes(x="#10: Check if pivot fits", y=score_activity_10)) +
  geom_col(mapping = aes(x="#11: Wobble or hammer pivot, if needed", y=score_activity_11)) +
  geom_col(mapping = aes(x="#12: Choose correct splint pen", y=score_activity_12)) +
  geom_col(mapping = aes(x="#13: Check if split pen closes properly", y=score_activity_13)) +
  geom_col(mapping = aes(x="#14: Put splint pen into pivot", y=score_activity_14)) +
  geom_text(mapping = aes(x="#01: Take egg", y=score_activity_01, label=round(score_activity_01,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#02: Choose egg of correct size", y=score_activity_02, label=round(score_activity_02,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#03: Check egg for outside damage", y=score_activity_03, label=round(score_activity_03,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#04: Check egg for inside damage", y=score_activity_04, label=round(score_activity_04,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#05: Place egg in right direction", y=score_activity_05, label=round(score_activity_05,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#06: Take correct pivot", y=score_activity_06, label=round(score_activity_06,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#07: Check pivot for damage", y=score_activity_07, label=round(score_activity_07,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#08: Disposed damaged pivot, if needed", y=score_activity_08, label=round(score_activity_08,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#09: Place pivot in right direction", y=score_activity_09, label=round(score_activity_09,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#10: Check if pivot fits", y=score_activity_10, label=round(score_activity_10,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#11: Wobble or hammer pivot, if needed", y=score_activity_11, label=round(score_activity_11,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#12: Choose correct splint pen", y=score_activity_12, label=round(score_activity_12,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#13: Check if split pen closes properly", y=score_activity_13, label=round(score_activity_13,2)), vjust=1.6, color="white") +
  geom_text(mapping = aes(x="#14: Put splint pen into pivot", y=score_activity_14, label=round(score_activity_14,2)), vjust=1.6, color="white") +
  
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#01: Take egg", ymin=score_activity_01_avg, ymax=score_activity_01_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#02: Choose egg of correct size", ymin=score_activity_02_avg, ymax=score_activity_02_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#03: Check egg for outside damage", ymin=score_activity_03_avg, ymax=score_activity_03_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#04: Check egg for inside damage", ymin=score_activity_04_avg, ymax=score_activity_04_avg)) +
    geom_errorbar(data=joined_s, color="red", mapping = aes(x="#05: Place egg in right direction", ymin=score_activity_05_avg, ymax=score_activity_05_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#06: Take correct pivot", ymin=score_activity_06_avg, ymax=score_activity_06_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#07: Check pivot for damage", ymin=score_activity_07_avg, ymax=score_activity_07_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#08: Disposed damaged pivot, if needed", ymin=score_activity_08_avg, ymax=score_activity_08_avg)) +
    geom_errorbar(data=joined_s, color="red", mapping = aes(x="#09: Place pivot in right direction", ymin=score_activity_09_avg, ymax=score_activity_09_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#10: Check if pivot fits", ymin=score_activity_10_avg, ymax=score_activity_10_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#11: Wobble or hammer pivot, if needed", ymin=score_activity_11_avg, ymax=score_activity_11_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#12: Choose correct splint pen", ymin=score_activity_12_avg, ymax=score_activity_12_avg)) +
    geom_errorbar(data=joined_s, color="red", mapping = aes(x="#13: Check if split pen closes properly", ymin=score_activity_13_avg, ymax=score_activity_13_avg)) +
  geom_errorbar(data=joined_s, color="red", mapping = aes(x="#14: Put splint pen into pivot", ymin=score_activity_14_avg, ymax=score_activity_14_avg)) +
  
  scale_x_discrete(name = "Activity") +
  scale_y_continuous(limits = c(0, 1), name = "Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Average score per activity (measured on Truss Corner #2)")

```